### 2015-04-15 contract-language.tex
Edits to figure atomicity implementation.

@@

The classification scheme, presented formally in Figure~\ref{sem:classify},
defines rules to judge the consistency class of a contact. For example, the
scheme classifies the \rcf{getBalance} contract ($\cv_{gb}$) from
\S~\ref{sec:motivation} as a {\sf\small CausallyConsistent} contract, because
the sequent $\Delta \vdash \ccc \Rightarrow \cv_{gb}$ is valid in first-order
logic (therefore, $\cv_{gb} \le \ccc$), whereas the sequent $\Delta \vdash \ecc
\Rightarrow \cv_{gb}$ is invalid (therefore, $\cv_{gb} \not\le \ecc$). Since we
confine our contract language to a decidable subset of the logic, validity
of such sequents can be decided mechanically allowing us to automate the
classification scheme in \name.

@@

\vspace{-2mm}
\begin{smathpar}
\renewcommand{\arraystretch}{1.2}
\begin{array}{rcl}
\R{Read Your Writes (RYW)} & \coloneqq & \forall a,b. ~\soo{a}{b} \Rightarrow \vis{a}{b} \\
\R{Monotonic Reads (MR)} & \coloneqq & \forall a,b,c. ~\vis{a}{b} \wedge \soo{b}{c} \\
 & & \quad \Rightarrow \vis{a}{c} \\
\R{Monotonic Writes (MW)} & \coloneqq & \forall a,b,c. ~\soo{a}{b} \wedge \vis{b}{c} \\
 & & \quad \Rightarrow \vis{a}{c} \\
\R{Writes Follow Reads (WFR)} & \coloneqq & \forall a,b,c,d. ~\vis{a}{b} \wedge \vis{c}{d} \\
 & & \wedge (\sooZ ~\cup =)(b,c) \Rightarrow \vis{a}{d}
\end{array}
\end{smathpar}

@@

In this scheme, the consistency level of an operation is any combination of the
above guarantees, which form a partially ordered consistency lattice show in
Figure~\ref{fig:lattice}. Each element in this lattice corresponds to a
store-consistency level, and is represented by its contract. An edge from an
upper level element to a lower level element corresponds to a weaker-than
relation between the corresponding contracts. Classifying a contract under
this scheme is a directed search in the lattice, starting from the bottom, and
determining the weakest consistency level under which the contract can be
satisfied. Under this scheme, \rcf{deposit} operations do not need any
guarantees, \rcf{getBalance} needs RYW and WFR ($\Delta \vdash \R{RYW} \wedge
\R{WFR} \Rightarrow \cv_{gb}$), and \rcf{withdraw} cannot be satisfied ($\Delta
\vdash \R{RYW} \wedge \R{MW} \wedge \R{MR} \wedge \R{WFR} \not\Rightarrow
\cv_{w}$).

>>>>

%  The above contract mandates that an effect $a$ must be visible to the current
%effect $\cureff$ if some effect $b$ that causally succeeds $a$ is also visible
%to $\cureff$. Thus, if every store replica always maintains and exposes a
%causal cut of updates to the client, then such a store will satisfy this
%contract. In such a system, an eventually consistent operation, such as
%\rcf{deposit}, can be satisfied as long as some replica is reachable.

@@

The classification scheme, presented formally in Figure~\ref{sem:classify},
defines rules to judge the consistency class of a contact. For example, the
scheme classifies the \rcf{getBalance} contract ($\cv_{gb}$) from
\S~\ref{sec:motivation} as a {\sf\small CausallyConsistent} contract, because
the sequent $\Delta \vdash \forall \cureff. \ccc \Rightarrow \cv_{gb}$ is valid
in first-order logic (therefore, $\cv_{gb} \le \ccc$), whereas the sequent
$\Delta \vdash \forall \cureff. \ecc \Rightarrow \cv_{gb}$ is invalid
(therefore, $\cv_{gb} \not\le \ecc$). Since we confine our contract language to
a decidable subset of the logic, validity of such sequents can be decided
mechanically allowing us to automate the classification scheme in \name.

@@

\vspace{-2mm}
\begin{smathpar}
\renewcommand{\arraystretch}{1.2}
\begin{array}{rcl}
\R{Read Your Writes (RYW)} & \coloneqq & \forall a. ~\soo{a}{\cureff} \Rightarrow \vis{a}{\cureff} \\
\R{Monotonic Reads (MR)} & \coloneqq & \forall a,b. ~\vis{a}{b} \wedge \soo{b}{\cureff} \\
 & & \quad \Rightarrow \vis{a}{\cureff} \\
\R{Monotonic Writes (MW)} & \coloneqq & \forall a,b. ~\soo{a}{b} \wedge \vis{b}{\cureff} \\
 & & \quad \Rightarrow \vis{a}{\cureff} \\
\R{Writes Follow Reads (WFR)} & \coloneqq & \forall a,b,c. ~\vis{a}{b} \wedge \vis{c}{\cureff} \\
 & & \wedge (\sooZ ~\cup =)(b,c) \Rightarrow \vis{a}{\cureff}
\end{array}
\end{smathpar}

@@

In this scheme, the consistency level of an operation is any combination of the
above guarantees, which form a partially ordered consistency lattice show in
Figure~\ref{fig:lattice}. Each element in this lattice corresponds to a
store-consistency level, and is represented by its contract. An edge from an
upper level element to a lower level element corresponds to a weaker-than
relation between the corresponding contracts. Classifying a contract under this
scheme is a directed search in the lattice, starting from the bottom, and
determining the weakest consistency level under which the contract can be
satisfied. Under this scheme, \rcf{deposit} operations do not need any
guarantees, \rcf{getBalance} needs RYW and WFR ($\cv_{gb} \le \R{RYW} \wedge
\R{WFR}$), and \rcf{withdraw} cannot be satisfied ($\cv_{w} \not\le \R{RYW}
\wedge \R{MW} \wedge \R{MR} \wedge \R{WFR} $).
